Chr7 hotspot analyses

### 2019-07-09 analysis/paper/Chr11.Rmd
updated Rmd files

```{r heat_pleio_stats, fig.height=4, fig.width = 6}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff}
foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff0}
foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  mutate(lod_diff = lod_diff * (lod_diff > 0)) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r, define_hld, eval = FALSE}
hld <- foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff)
plotly::plot_ly(as.data.frame(hld), z = as.data.frame(hld)$lod_diff, type = "heatmap")
```

@@

```{r, loddiff_clust}
foo %>%
  select(1, 2, 4) %>% # choose lod_diff as the stat of interest
  tibble_to_matrix() %>%
  heatmap.2( 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, 
          cexRow = 0.4
      )

@@

```{r, loddiffprop_clust}
foo %>%
  select(1, 2, 5) %>% # choose lod_diff_proportion as stat of interest
  tibble_to_matrix() %>%
  heatmap.2( 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, cexRow = 0.4
      )

@@

```{r threshold_clust}
med_thresh <- 2
foomat <- foo %>%
  select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
  apply(FUN = function(x) x <= med_thresh, X = foomat, MARGIN = 2) %>%
    d3heatmap()
```

```{r}
foo %>%
  select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix() %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

@@

>>>>

```{r heat_pleio_stats, fig.height=4, fig.width = 6}
foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff}
foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff0}
foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  mutate(lod_diff = lod_diff * (lod_diff > 0)) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r, define_hld, eval = FALSE}
hld <- foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff)
plotly::plot_ly(as.data.frame(hld), z = as.data.frame(hld)$lod_diff, type = "heatmap")
```

@@

```{r, loddiff_clust}
foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as the stat of interest
  tibble_to_matrix() %>%
  heatmap.2( 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, 
          cexRow = 0.4
      )

@@

```{r, loddiffprop_clust}
foo %>%
  dplyr::select(1, 2, 5) %>% # choose lod_diff_proportion as stat of interest
  tibble_to_matrix() %>%
  heatmap.2( 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, cexRow = 0.4
      )

@@

```{r threshold_clust}
med_thresh <- 2
foomat <- foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
  apply(FUN = function(x) x <= med_thresh, X = foomat, MARGIN = 2) %>%
    d3heatmap()
```

```{r}
foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix() %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

@@

## Pleiotropy test results for *all* trait pairs

```{r all-pleio}
foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

## Mediation (LOD diff) results (truncated at zero) for local-nonlocal pairs

```{r med-trunc-heat}
foo %>%
  dplyr::select(1, 2, 4) %>%
  mutate(lod_diff_trunc = lod_diff * (lod_diff > 0)) %>%
  dplyr::select(-3) %>%
  tibble_to_matrix(symmetric = FALSE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

## Mediation (LOD diff proportion) results (truncated at zero) for local-nonlocal pairs

```{r med-prop-trunc-heat}
foo %>%
  dplyr::select(1, 2, 5) %>%
  mutate(lod_diff_prop_trunc = lod_diff_proportion * (lod_diff_proportion > 0)) %>%
  dplyr::select(-3) %>%
  tibble_to_matrix(symmetric = FALSE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

### 2019-07-09 analysis/paper/Chr13-hclusterings.Rmd
updated Rmd files

---
title: "Chr11 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
keller_mediator <- "Sat2"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

@@

```{r rafalib-plot2}
cols <- 1 + (all_all_hclust$labels %in% bar$nonlocal_symbol)
cols[all_all_hclust$labels == keller_mediator] <- 3
# dendro plot
all_all_hclust %>%
  rafalib::myplclust(cex = 0.2, 
                     lab.col = cols, 
                     main = paste0("Chr", 
                                   hot_chr, 
                                   " dendrogram"
                                   ), 
                     sub = "pleiotropy test statistics"
                       )

>>>>

---
title: "Chr13 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 13
run_num <- 9931
hot_mid <- 112.5
keller_mediator <- "Il6st"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

@@

```{r rafalib-plot2}
cols <- 1 + (all_all_hclust$labels %in% bar$nonlocal_symbol)
cols[all_all_hclust$labels == keller_mediator] <- 3
# dendro plot
# dendro plot
all_all_hclust %>%
  rafalib::myplclust(cex = 0.2, 
                     lab.col = cols, 
                     main = paste0("Chr", 
                                   hot_chr, 
                                   " dendrogram"
                                   ), 
                     sub = "pleiotropy test statistics"
                       )

### 2019-07-09 analysis/paper/Chr2-hclusterings.Rmd
updated Rmd files

---
title: "Chr11 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
keller_mediator <- "Sat2"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

@@

```{r}
foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
```

>>>>

---
title: "Chr2 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 2
run_num <- 9941
hot_mid <- 165.5
keller_mediator <- "Hnf4a"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

@@

### 2019-07-09 analysis/paper/Chr2.Rmd
updated Rmd files

```{r read_pleio_results}
pleio_file <- "_cache/Chr2_pleio.rds"
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r heat_pleio_stats}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff}
foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff0}
foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  mutate(lod_diff = lod_diff * (lod_diff > 0)) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r, define_hld, eval = FALSE}
hld <- foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff)
plotly::plot_ly(as.data.frame(hld), z = as.data.frame(hld)$lod_diff, type = "heatmap")
```

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- "_cache/Chr2_pleio_local.rds"
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

@@

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- "_cache/Chr2_pleio_nonlocal.rds"
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

>>>>

```{r read_pleio_results}
pleio_file <- "_cache/Chr2_pleio.rds"
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    dplyr::select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r heat_pleio_stats}
foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff}
foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff0}
foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  mutate(lod_diff = lod_diff * (lod_diff > 0)) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r, define_hld, eval = FALSE}
hld <- foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff)
plotly::plot_ly(as.data.frame(hld), z = as.data.frame(hld)$lod_diff, type = "heatmap")
```

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- "_cache/Chr2_pleio_local.rds"
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    dplyr::select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

@@

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- "_cache/Chr2_pleio_nonlocal.rds"
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]],
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    dplyr::select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

### 2019-07-09 analysis/paper/Chr5-hclusterings.Rmd
updated Rmd files

---
title: "Chr11 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
keller_mediator <- "Sat2"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

>>>>

---
title: "Chr5 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 5
run_num <- 9901
hot_mid <- 146
keller_mediator <- "Pdx1"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

### 2019-07-09 analysis/paper/Chr7-hclusterings.Rmd
updated Rmd files

---
title: "Chr5 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 5
run_num <- 9901
hot_mid <- 146
keller_mediator <- "Pdx1"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

>>>>

---
title: "Chr7 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 7
run_num <- 9911
hot_mid <- 46
keller_mediator <- "Fam83e"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

### 2019-07-09 analysis/paper/Chr7.Rmd
updated Rmd files

```{r local-local-pleio}
local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap()
```

@@

```{r nonlocal-nonlocal-pleio}
nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

>>>>

```{r local-local-pleio}
local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3, symm = TRUE)

```{r local-local-hclust}
l_l_hclust <- local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  (function(x){x[is.null(x)] <- 0; return(x)}) %>%
  dist() %>%
  hclust()
l_l_hclust %>%  
  cutree(h = 40) %>% table()

l_l_hclust %>%
  rafalib::myplclust(cex = 0.4, lab.col = 1 + as.numeric(l_l_hclust$labels == keller_mediator))
```

@@

```{r nonlocal-nonlocal-pleio}
nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3, symm = TRUE)
```

```{r nl-nl-hclust}
nl_nl_hclust <- nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  dist() %>% 
  hclust()
plot(nl_nl_hclust, cex = 0.2)
nl_nl_hclust %>%
  cutree(h = 10) %>%
  table()
```

```{r rafalib-plot1}
# make color labels for dendro plot
precols <- tibble(nonlocal_symbol = nl_nl_hclust$labels) %>%
  left_join(bar) %>% # bar has local_symbol set to keller_mediator
  dplyr::arrange(match(x = nonlocal_symbol, table = nl_nl_hclust$labels))
# check ordering of nonlocal_symbol against nl_nl_hclust$labels
# IT'S THE SAME, but only after including the call to dplyr::arrange()

cols <- 1 + (precols$lod_diff > 1.5)
# dendro plot
nl_nl_hclust %>%
  rafalib::myplclust(cex = 0.3, lab.col = cols)
```

## Pleiotropy test results for *all* trait pairs

```{r all-pleio}
foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

```{r, all-all-hclust}
all_all_hclust <- foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  dist() %>%
  hclust()
```

```{r rafalib-plot2}
cols <- 1 + (all_all_hclust$labels %in% bar$nonlocal_symbol)
cols[all_all_hclust$labels == keller_mediator] <- 3
# dendro plot
all_all_hclust %>%
  rafalib::myplclust(cex = 0.2, lab.col = cols)

## Mediation (LOD diff) results (truncated at zero) for local-nonlocal pairs

```{r med-trunc-heat}
foo %>%
  dplyr::select(1, 2, 4) %>%
  mutate(lod_diff_trunc = lod_diff * (lod_diff > 0)) %>%
  dplyr::select(-3) %>%
  tibble_to_matrix(symmetric = FALSE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

## Mediation (LOD diff proportion) results (truncated at zero) for local-nonlocal pairs

```{r med-prop-trunc-heat}
foo %>%
  dplyr::select(1, 2, 5) %>%
  mutate(lod_diff_prop_trunc = lod_diff_proportion * (lod_diff_proportion > 0)) %>%
  dplyr::select(-3) %>%
  tibble_to_matrix(symmetric = FALSE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```
